Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-18 Grassmannian_cells.tex
Some clean-up and reorganization in 3.1, more polishing needed

\begin{lemma}
  \label{le:lifts of transjectives}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$. Any lift of a preprojective (or preinjective) representation is preprojective (preinjective). 
 % \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives both claims.
\end{proof}

@@

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
\sayD{Specific reference needed?}
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ and/or $\rep \hat Q$ by $\rep\widetilde Q$.
\end{theorem}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

@@

Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  \sayD{Proof needed}\sayT{explain $\tau V$. Do we need this?}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  But observe that we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

\begin{corollary}\sayT{proof?}
  For $V,W\in \Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

\begin{lemma}
  \label{le:more truncated homomorphisms}
  For $W\in \Gr(H_m)$, $m\ge2$, the following hold:
  \begin{enumerate}
    \item $\Hom(P_{m-1},P_m^{\bar{W}})\cong W^*$;
    \item $\Hom(P_{m+1},P_m^{\bar{W}})\cong (H_m/W)^*$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  By Lemma~\ref{le:preprojective homomorphism duality}, we have $H_{m-1}\cong H_m^*$ and $\bar{W}\cong(H_m/W)^*$.
  Then Lemma~\ref{le:truncated homomorphisms} gives the isomorphism
  \[\Hom(P_{m-1},P_m^{\bar{W}})\cong H_{m-1}/\bar{W}\cong H_m^*/(H_m/W)^*\cong W^*.\]

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:unique preprojective morphism}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{remark}
  For $W\in \Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension-one subspace $V\subset H_m$ containing $W$.
  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
\end{remark}
\begin{corollary}
  For $V,W\in \Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}

\begin{lemma}\sayT{proof? Special case of 3.23?}
  For $V,W\in \Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
\end{lemma}

\begin{lemma}
  For $m\ge2$ and $V\in \Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.  More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
\end{lemma}
\begin{proof}
  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
  This proves the first claim.

  It remains to show that $\tilde V=\bar{\bar{V}}$.
\end{proof}

\begin{lemma}
  \label{le:truncated exact sequences}
  For $V\in \Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
\end{lemma}
\begin{proof}
  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
  It follows that the sequence
  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
  is exact.
  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.

  For the final claim we observe that, for another direct sum decomposition $V=U'\oplus W'$, the representations $P_{m+1}^U\oplus P_{m+1}^W$ and $P_{m+1}^{U'}\oplus P_{m+1}^{W'}$ are isomorphic if and only if the direct sum decompositions $V=U\oplus W$ and $V=U'\oplus W'$ are the same up to permutation of summands.
\end{proof}

\sayD{The next result needs some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
\begin{lemma}
  For $V\in \Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  This occurs (?) if and only if the composed morphism
  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
  is nonzero.
\end{lemma}
\begin{proof}
  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  if and only if the lower pushout sequence below splits: 
  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.

  and
  \[\xymatrix{0 \ar[r] & \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1},X) \ar[r] & \Ext(P_m\otimes V,X) \ar[r] &  0}.\]
\end{proof}

>>>>

\begin{lemma}
  \label{le:lifts of transjectives}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$. Any lift of a preprojective (or preinjective) representation is preprojective (preinjective). 
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives both claims.
\end{proof}

@@

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ and/or $\rep \hat Q$ by $\rep\widetilde Q$.
\end{theorem}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write $$R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})$$ for the affine space of representations of dimension $d$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@
